---
title: "R Notebook"
author: 'Alyssa Knapp'
date: '11/12/20'
output: html_notebook
---


```{r}
rm(list = ls())

library(mosaic)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(readxl)
```

Data Source 1: 
```{r}
UFO <- read.csv("scrubbed.csv", header = TRUE)
```

Data Source 2: 
```{r}
UFO2 <- read_excel("UFOs_coord.xlsx")
```


## Become acquainted with data sources 

Data Source 1

1. I found this data source from kaggle.com

2. This dataset is maintained by the National UFO Reporting Center (NUFORC)

3. This data was compiled in 2014 by Sigmond Axel, using 80,000 reports of UFO sightings from the last century. It was collected to 

4. 

5. 


Data Source 2

1. I found this data source from data.world

2. This dataset is maintained by data engineer, Alejandro Manuel Arranz Lopez 

3. This data was collected in 2016 by the National UFO reporting center, specifically from the US/Canada reports. It was collected to 

4. 

5. 



## Statement of Research Question

**Which areas of the United States experience the most UFO sightings?**


## Examine Data Source 1

```{r}
View(UFO)
glimpse(UFO)

favstats(~state, data = UFO)
favstats(~city, data = UFO)
favstats(~country, data = UFO)
summary(UFO)
```

There are 11 variables and 80,332 cases. 


## Address Research Question

```{r}
UFO_US <- mutate(UFO, country = "us")
View(UFO_US)
```

```{r}

```


```{r}
UFO_US %>%
  ggplot(aes(x=state)) + 
  geom_density(color = "blue", fill = "blue", alpha = 0.75)
  xlab("States that recorded UFO sightings")
```


## Discover features in the data that may impact modeling decisions

```{r}

```






## Examine Data Source 2

```{r}
View(UFO2)
glimpse(UFO2)

summary(UFO2)
```

There are 8 variables and 5,177 cases. 


## Address Research Question

```{r}
UFO2_US <- mutate(UFO2, Country = "USA")
View(UFO2_US)
```


```{r}

```


## Discover features in the data that may impact modeling decisions

```{r}

```


## Joining datasets

```{r}
UFO_data <-
  UFO %>%
  left_join(UFO2, by = 
```

