---
title: "R Notebook"
author: 'Alyssa Knapp'
date: '11/12/20'
output: html_notebook
---


```{r}
rm(list = ls())

library(mosaic)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(readxl)
```

Data Source 1: 
```{r}
UFO <- read.csv("scrubbed.csv", header = TRUE)
```

Data Source 2: 
```{r}
UFO2 <- read_excel("UFOs_coord.xlsx")
```


## Become acquainted with data sources 

Data Source 1

1. I found this data source from kaggle.com

2. This dataset is maintained by the National UFO Reporting Center (NUFORC)

3. This data was compiled in 2014 by Sigmond Axel, using 80,000 reports of UFO sightings from the last century. It was collected to 

4. There are 80,332 cases in the original dataset. Each case represents a UFO sighting and its characteristics in a particular country (+ city and/or state). 

5. I plan to use the variables: "country", "shape", "state" and "longitude" 


Data Source 2

1. I found this data source from data.world

2. This dataset is maintained by data engineer, Alejandro Manuel Arranz Lopez 

3. This data was collected in 2016 by the National UFO reporting center, specifically from the US/Canada reports. It was collected to 

4. There are 5,177 cases in the original dataset. Each case represents a UFO sighting and its characteristics in a particular country (+ city and/or state). 

5. I plan to use the variables: "Country", "State", "Shape", and "Longitude." 



## Statement of Research Question

**Are U.S. states in the West region more likely to experience UFOs, shaped like disks, for greater durations of time (in seconds)?**


**Are U.S. states in the West region more likely to experience UFOs, shaped like disks, at greater longitudes?**

**Are UFOs shaped like disks most often sighted in the West region of the United States and at the greatest longitudes?** This one!


## Data Source 1

### Examining Dataset

```{r}
View(UFO)
glimpse(UFO)

favstats(~state, data = UFO)
favstats(~city, data = UFO)
favstats(~country, data = UFO)
favstats(~longitude, data = UFO)

summary(UFO)
```



### Simplifying Data

```{r}
as.character("state")

a <- c("me","nh","vt","ri","ct","ny","pa","nj")
b <- c("wi","mi","il","oh","nd","sd","ne","ks","mn","ia","mo")
c <- c("de","md","va","wv","nc","sc","ga","fl","ky","ms","al","ok","tx","ar","la")
d <- c("id", "mt", "wy", "nv", "ut", "co", "az", "nm", "ak", "wa", "or", "ca", "hi")

xx <- c(a, b, c, d)
yy <- ifelse(xx %in% c(a), "Northeast", ifelse(xx %in% c(b), "Midwest", ifelse(xx %in% c(c), "South", "West")))

# Region <- UFO_US %>%
#  mutate(region = ifelse(state %in% c("me","nh","vt","ri","ct","ny","pa","nj"), "Northeast",
# ifelse(state %in% c("wi","mi","il","oh","nd","sd","ne","ks","mn","ia","mo"),"Midwest", ifelse(state %in% c("de","md","va","wv","nc","sc","ga","fl","ky","ms","al","ok","tx","ar","la"), "South", "West"))))

View(UFO_US)
```


```{r}
UFO_US <- 
  UFO %>%
  filter(country == "us") %>%
  filter(shape == c("circle", "light", "disk")) %>%
  filter(state != "pr")

View(UFO_US)
str(UFO_US)
```



### Exploring 'shape'

```{r}
ggplot(data = UFO_US) + 
  geom_bar(mapping = aes(x= shape))
```


## Exploring 'state'

```{r fig.width = 12}
ggplot(data = UFO_US) + 
  geom_bar(mapping = aes(x= shape)) + facet_wrap(~state)

ggplot(data = UFO_US) + 
  geom_bar(aes(x = state)) 
```



## Exploring 'longitude'

```{r}
ggplot(data = UFO_US, mapping = aes(x = longitude)) +
  geom_histogram(binwidth = 0.5)
```


```{r fig.width = 14}
ggplot(data = UFO_US, aes(y = longitude, x = state)) + 
  geom_line()
```



```{r fig.height = 12, fig.width = 14}

longitude <- 
  ggplot(UFO_US, aes(x= state, y = longitude, fill= shape))+
  geom_bar(width = 1, stat = "identity")

longitude
```




## Data Source 2

## Examining dataset

```{r}
View(UFO2)
glimpse(UFO2)
str(UFO2)
summary(UFO2)
```


### Simplifying Dataset

```{r}
UFO2_US <- 
  UFO2 %>%
  filter(Country == "USA") %>%
  filter(Shape == c("Circle", "Light", "Disk"))

View(UFO2_US)
str(UFO2_US)
```


### Exploring 'Shape'

```{r}
ggplot(data = UFO2_US) + 
  geom_bar(mapping = aes(x= Shape)) 
```



## Exploring 'State'

```{r fig.width = 12}

ggplot(data = UFO2_US) + 
  geom_bar(mapping = aes(x= Shape)) + facet_wrap(~State)

ggplot(data = UFO2_US) + 
  geom_bar(aes(x = State)) 
```



## Exploring 'lng' (longitude)

```{r}
ggplot(data = UFO2_US, mapping = aes(x = lng)) +
  geom_histogram(binwidth = 0.5)
```


```{r fig.width = 14}
ggplot(data = UFO2_US, aes(y = lng, x = State)) + 
  geom_line()
```



```{r fig.height = 12, fig.width = 14}

lng <- 
  ggplot(UFO2_US, aes(x= State, y = lng, fill= Shape))+
  geom_bar(width = 1, stat = "identity")

lng
```



